\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-23 draft.tex
complete proof of prop:2NNB

The next-to-last principal minor is the 3x3 matrix that is the upper-lefthand corner of this matrix. This determinant should be non-negative but is identically equal to zero because of the first row of zeros. This therefore provides no restrictions on the problem.\footnote{In the case where it is the non-negativity constraint on either $b_0$ or $b_{-.5}$ that binds, this condition \textit{does} imply an extra constraint. When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b_{-.5}^2} \geq0$, i.e. $Y\leq 0$. When $b_{-.5}=0$, the extra condition is that $X\leq 0$.}

@@

In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_{-\frac{1}{2}}$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below). Note that once this is known, one can go back to, for instance, Equations~\ref{eq:baseX} and substitute for one of the variables. Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.

$\hfill\blacksquare$

>>>>

The next-to-last principal minor is the 3x3 matrix that is the upper-lefthand corner of this matrix. This determinant should be non-negative but is identically equal to zero because of the first row of zeros. This therefore provides no restrictions on the problem.\footnote{In the case where it is the non-negativity constraint on either $b_0$ or $b_{-.5}$ that binds, this condition \textit{does} imply an extra constraint. When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b_{-.5}^2} \geq0$, i.e. $Y\leq 0$. When $b_{-.5}=0$, the extra condition is that $X\leq 0$.\label{fn:extra}}

@@

In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_\frac{1}{2}$, there are three possibilities, $Z=0$, $Z>0$ and $Z<0$. I will take each in turn.
\begin{enumerate}
	\item $Z = 0$, $e^Z = 1$. Then the only values of $X$ and $Y$ with which both Equation~\ref{eq:1} and \ref{eq:2} are consistent are $X=Y$.\footnote{Note that this is the only case in which $e^{-2Z} =1$, i.e. $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0} = 0$. In the other two cases, the right hand side of \ref{eq:soc} is strictly positive so that the two second derivatives on the left hand side must be either both positive or both negative. This means that $X$ and $Y$ must be either both positive or both negative.}
	\item $Z > 0$, $e^Z > 1$. In this case, $X$ and $Y$ must be positive since they are greater than $Z$. Equation~\ref{eq:1} is consistent only with $Y\geq X\geq 0$, while Equation~\ref{eq:2} is consistent with $X \geq Y \geq 0$. Since both equations must hold, we have $X=Y \geq 0$.
	\item $Z < 0$, $e^Z < 1$. In this case, Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$ or $0 \geq Y \geq X$. Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$ or $0 \geq X \geq Y$. Since both equations must hold, we have either $X=Y \geq 0$ or $X=Y \leq 0$.
\end{enumerate}
		In any case, it must be that $X = Y$. Similar, slightly simpler proofs go through when the zero bribe is for either of the other two legislators because of the extra condition described in Footnote~\ref{fn:extra}. $\hfill\blacksquare$
